### 2020-05-27 writeup/experiments.tex
re structure
reorg

\section{Experiments}

@@

\subsection{Results and Analysis}

\textbf{A metric to determine positive versus negative transfer.}
We propose a simple metric to determine whether multi-task learning performs better than single-task learning.
The metric is as follows.
First, we train 2 single-task models on 2 separate tasks.
We take the prediction accuracy of the two tasks.
Let $\tau$ be a fixed threshold.
If the accuracy of the source task is higher than the accuracy of the target task by $\tau$, then we predict positive transfer.
On the other hand, if the accuracy of the source task is lower than the accuracy of the target task by $\tau$, then we predict negative transfer.

@@

\textbf{Multi-task learning provides labeled data efficiency.}
We measure the data efficiency ratio on text classification tasks.
We find that by performing multi-task learning, only 40$\%$ of the data is needed to achieve comparable performance to single-task learning over all six tasks.

\textbf{Covariance alignment provides more improvement when data size is imbalanced.}
We validate that the performance of aligning task covariances depends on the size of source task data.
Recall that the covariance alignment procedure in \cite{WZR20} adds an additional module between the word embedding representation and the shared module.

@@

>>>>

\section{Practical Implications for Multi-Task Learning}

@@

\subsection{Detecting and Improving Negative Effects}

\textbf{A Metric to Determine Positive or Negative Transfer}
We propose a simple metric to determine whether multi-task learning performs better than single-task learning.
The metric is as follows.
First, we train 2 single-task models on 2 separate tasks.
We take the prediction accuracy of the two tasks.
Let $\tau$ be a fixed threshold.
If the accuracy of the source task is higher than the accuracy of the target task by $\tau$, then we predict positive transfer.
On the other hand, if the accuracy of the source task is lower than the accuracy of the target task by $\tau$, then we predict negative transfer.

@@

\textbf{Covariance Alignment for Imbalanced Tasks with Covariate Shift.}
We validate that the performance of aligning task covariances depends on the size of source task data.
Recall that the covariance alignment procedure in \cite{WZR20} adds an additional module between the word embedding representation and the shared module.

@@

\subsection{Validating Theoretical Observations}

\textbf{Benefits of multi-task learning.}

\textit{Improving labeled data efficiency.}
We measure the data efficiency ratio on text classification tasks.
We find that by performing multi-task learning, only 40$\%$ of the data is needed to achieve comparable performance to single-task learning over all six tasks.

\textit{Transferring from a high accuracy to low accuracy.}

\textbf{Causes of negative transfer.}
